---
title: "Power and PAA results"
author:
   - name: Jordan Revol, jordan.revol@kuleuven.be, KU Leuven
   - name: Yong Zang, yong.zhang@rug.nl, University of Groningen
date: "`r Sys.Date()`"
output: 
    html_document:
        toc: true
        toc_depth: 3
        number_sections: true
        toc_float: true
        df_print: paged
---

# Introduction

This document is the results of the simulation from the manuscript by Zhang et al. (2021) "Meeting the Bare Minimum: Quality Assessment of Idiographic Temporal Networks Using Power Analysis and Predictive Accuracy Analysis". 


# Import

Load libraries
```{r, warning=FALSE, message=FALSE}
library(dplyr)
library(tidyr)
library(data.table)
library(ggplot2)
library(kableExtra)
library(stringr)
library(graphicalVAR)
library(qgraph)
library(fastmatrix)
```


Import data
```{r}
df_res <- read.csv("data/df_results.csv")
load("data/list_param.rda")
```


# Plot

Figures of the VAR(1) networks based on the parameters of the different models investigated in the article. 
The figures can be found in the folder 'figures/network/'. 


## Illustration

```{r}
VAR_phi = list_param$illustration$phi

# Visualize the temporal network
qgraph(t(VAR_phi),
       node.width = 1.6,
       node.height = 1.6,
       mar = c(6, 6, 6, 6),
       # layout = matrix(c(0, 1, 0,
       #                   0, 0, 0,
       #                   2, 0, 3),
       #                 nrow = 3, byrow = T),
       layout = "groups",
       theme = "colorblind",
       negDashed = T,
       edge.labels = T,
    #    labels = c("Relaxed",
    #               "Sad",
    #               "Nervous",
    #               "Concen- \ntration",
    #               "Tired",
    #               "Rumi- \nnation",
    #               "Bodily \ndiscomfort"),
       label.prop = 0.9,
       label.fill.horizontal = .8,
       label.fill.vertical = .8,
       label.scale = TRUE,
       fade = FALSE,
       filetype = "png",
       filename = "figures/network/illustration")
```


## Epskamp, van Borkulo, et al., 2018

```{r}
VAR_phi = list_param$epskamp$phi

# Visualize the temporal network
qgraph(t(VAR_phi),
       node.width = 1.6,
       node.height = 1.6,
       mar = c(6, 6, 6, 6),
       # layout = matrix(c(0, 1, 0,
       #                   0, 0, 0,
       #                   2, 0, 3),
       #                 nrow = 3, byrow = T),
       layout = "groups",
       theme = "colorblind",
       negDashed = T,
       edge.labels = T,
       labels = c("Relaxed",
                  "Sad",
                  "Nervous",
                  "Concen- \ntration",
                  "Tired",
                  "Rumi- \nnation",
                  "Bodily \ndiscomfort"),
       label.prop = 0.9,
       label.fill.horizontal = .8,
       label.fill.vertical = .8,
       label.scale = TRUE,
       fade = FALSE,
       filetype = "png",
       filename = "figures/network/epskamp_vanBorkulo_2018_colorblind")
```


## Bak2016 Full relaspe

```{r}
# Network visualization
reg_mat <- list_param$bak2016_full$phi
p_mat <- list_param$bak2016_full$p_mat
plot_reg_mat <- hadamard(reg_mat, 1*(p_mat < .05))

qgraph(t(plot_reg_mat),
       node.width = 1.6,
       node.height = 1.6,
       mar = c(6, 6, 6, 6),
       # layout = matrix(c(0, 1, 0,
       #                   0, 0, 0,
       #                   2, 0, 3),
       #                 nrow = 3, byrow = T),
       layout = "groups",
       theme = "colorblind",
       title = "a) Full relapse",
       negDashed = T,
       edge.labels = T,
       labels = c("Down",
                  "Relaxed",
                  "Paranoia",
                  "Hearing \nvoices",
                  "Loss of \ncontrol"),
       label.prop = 0.9,
       label.fill.horizontal = .8,
       label.fill.vertical = .8,
       label.scale = TRUE,
       fade = FALSE,
       filetype = "png",
       filename = "figures/network/Bak2016_full_relapse_combine")
```


```{r}
# Network visualization
reg_mat <- list_param$bak2016_full_plus1se$phi
p_mat <- list_param$bak2016_full_plus1se$p_mat
plot_reg_mat <- hadamard(reg_mat, 1*(p_mat < .05))

qgraph(t(plot_reg_mat),
       node.width = 1.6,
       node.height = 1.6,
       mar = c(6, 6, 6, 6),
       # layout = matrix(c(0, 1, 0,
       #                   0, 0, 0,
       #                   2, 0, 3),
       #                 nrow = 3, byrow = T),
       layout = "groups",
       theme = "colorblind",
       title = "x) Full relapse estimates +1se",
       negDashed = T,
       edge.labels = T,
       labels = c("Down",
                  "Relaxed",
                  "Paranoia",
                  "Hearing \nvoices",
                  "Loss of \ncontrol"),
       label.prop = 0.9,
       label.fill.horizontal = .8,
       label.fill.vertical = .8,
       label.scale = TRUE,
       fade = FALSE,
       filetype = "png",
       filename = "figures/network/Bak2016_full_relapse_combine_plus1se")


```




```{r}
# Network visualization
reg_mat <- list_param$bak2016_full_minus1se$phi
p_mat <- list_param$bak2016_full_minus1se$p_mat
plot_reg_mat <- hadamard(reg_mat, 1*(p_mat < .05))

qgraph(t(plot_reg_mat),
       node.width = 1.6,
       node.height = 1.6,
       mar = c(6, 6, 6, 6),
       # layout = matrix(c(0, 1, 0,
       #                   0, 0, 0,
       #                   2, 0, 3),
       #                 nrow = 3, byrow = T),
       layout = "groups",
       theme = "colorblind",
       title = "x) Full relapse estimates -1se",
       negDashed = T,
       edge.labels = T,
       labels = c("Down",
                  "Relaxed",
                  "Paranoia",
                  "Hearing \nvoices",
                  "Loss of \ncontrol"),
       label.prop = 0.9,
       label.fill.horizontal = .8,
       label.fill.vertical = .8,
       label.scale = TRUE,
       fade = FALSE,
       filetype = "png",
       filename = "figures/network/Bak2016_full_relapse_combine_minus1se")


```



## bak2016_relapse

```{r}
# Network visualization
reg_mat <- list_param$bak2016_relapse$phi
p_mat <- list_param$bak2016_relapse$p_mat
plot_reg_mat <- hadamard(reg_mat, 1*(p_mat < .05))

qgraph(t(plot_reg_mat),
       node.width = 1.6,
       node.height = 1.6,
       mar = c(6, 6, 6, 6),
       # layout = matrix(c(0, 1, 0,
       #                   0, 0, 0,
       #                   2, 0, 3),
       #                 nrow = 3, byrow = T),
       layout = "groups",
       theme = "colorblind",
       title = "Full relapse",
       negDashed = T,
       edge.labels = T,
       labels = c("Down",
                  "Relaxed",
                  "Paranoia",
                  "Hearing \nvoices",
                  "Loss of \ncontrol"),
       label.prop = 0.9,
       label.fill.horizontal = .8,
       label.fill.vertical = .8,
       label.scale = TRUE,
       fade = FALSE,
       filetype = "png",
       filename = "figures/network/Bak2016_relapse")
```



## Bak2016 stable

```{r}
# Network visualization
reg_mat <- list_param$bak2016_stable$phi
p_mat <- list_param$bak2016_stable$p_mat
plot_reg_mat <- hadamard(reg_mat, 1*(p_mat < .05))

qgraph(t(plot_reg_mat),
       node.width = 1.6,
       node.height = 1.6,
       mar = c(6, 6, 6, 6),
       # layout = matrix(c(0, 1, 0,
       #                   0, 0, 0,
       #                   2, 0, 3),
       #                 nrow = 3, byrow = T),
       title = "a) Point estimates",
       layout = "groups",
       theme = "colorblind",
       negDashed = T,
       edge.labels = T,
       labels = c("Down",
                  "Relaxed",
                  "Paranoia",
                  "Hearing \nvoices",
                  "Loss of \ncontrol"),
       label.prop = 0.9,
       label.fill.horizontal = .8,
       label.fill.vertical = .8,
       label.scale = TRUE,
       fade = FALSE,
       filetype = "png",
       filename = "figures/network/Bak2016_stable")
```

```{r}
# Network visualization
reg_mat <- list_param$bak2016_stable_plus1se$phi
p_mat <- list_param$bak2016_stable_plus1se$p_mat
plot_reg_mat <- hadamard(reg_mat, 1*(p_mat < .05))

qgraph(t(plot_reg_mat),
       node.width = 1.6,
       node.height = 1.6,
       mar = c(6, 6, 6, 6),
       # layout = matrix(c(0, 1, 0,
       #                   0, 0, 0,
       #                   2, 0, 3),
       #                 nrow = 3, byrow = T),
       title = "b) 1 SE larger",
       layout = "groups",
       theme = "colorblind",
       negDashed = T,
       edge.labels = T,
       labels = c("Down",
                  "Relaxed",
                  "Paranoia",
                  "Hearing \nvoices",
                  "Loss of \ncontrol"),
       label.prop = 0.9,
       label.fill.horizontal = .8,
       label.fill.vertical = .8,
       label.scale = TRUE,
       fade = FALSE,
       filetype = "png",
       filename = "figures/network/Bak2016_stable_plus1se")
```




```{r}
# Network visualization
reg_mat <- list_param$bak2016_stable_minus1se$phi
p_mat <- list_param$bak2016_stable_minus1se$p_mat
plot_reg_mat <- hadamard(reg_mat, 1*(p_mat < .05))

qgraph(t(plot_reg_mat),
       node.width = 1.6,
       node.height = 1.6,
       mar = c(6, 6, 6, 6),
       # layout = matrix(c(0, 1, 0,
       #                   0, 0, 0,
       #                   2, 0, 3),
       #                 nrow = 3, byrow = T),
       title = "c) 1 SE smaller",
       layout = "groups",
       theme = "colorblind",
       negDashed = T,
       edge.labels = T,
       labels = c("Down",
                  "Relaxed",
                  "Paranoia",
                  "Hearing \nvoices",
                  "Loss of \ncontrol"),
       label.prop = 0.9,
       label.fill.horizontal = .8,
       label.fill.vertical = .8,
       label.scale = TRUE,
       fade = FALSE,
       filetype = "png",
       filename = "figures/network/Bak2016_stable_minus1se")
```











# All results

Below, you can find the results of the power and PAA analysis for the different models. The tables are organized by model. 
For each model, you can investigate, across different number of timepoints, the power associated to each parameters and the SPAP score.
When there is a parenthesis, the first value corresponds to the performance metric (i.e., power or SPAP) for the -1SE parameter values and the second value corresponds to the +1SE parameter values (e.g., (-1SE, +1SE)) of the models. 

```{r, fig.height=20, fig.width=17}
pow_table = function(df, name="epskamp"){
    df = df[df$name==name,]

    # Remove columns which contains only 'NA' values
    df <- df[, colSums(is.na(df)) != nrow(df)]
    # Order based on timepoint
    df <- df[order(df$timepoint),]
    
    # Convert to character
    df[,4:ncol(df)] = lapply(df[,4:ncol(df)], as.character)
    # add star is number higher than .8
    df[,4:ncol(df)] = lapply(df[,4:ncol(df)], function(x) ifelse(as.numeric(x) > .8, paste0(x, "\\*"), x))

    kbl(df, full_width = FALSE, escape = FALSE) %>%
        kable_classic()
}


# Table with merged columns: est (+1SE, -1SE)
pow_table_merge = function(df, name_select="bak2016_full", target="pow", pivot=FALSE){

    df = df %>% filter(grepl(name_select, df$name)) %>%
        mutate(name = str_remove(name, paste0(name_select)),
               name = case_when(name == "_minus1se" ~ "-1SE",
                                name == "_plus1se" ~ "+1SE",
                                TRUE ~ "est"))
    
    # Remove columns which contains only 'NA' values
    df <- df[, colSums(is.na(df)) != nrow(df)]

    # Round the values
    df[,4:ncol(df)] = round(df[,4:ncol(df)], 3)

    # Convert to character
    df[,4:ncol(df)] = lapply(df[,4:ncol(df)], as.character)
    # add star is number higher than .8
    df[,4:ncol(df)] = lapply(df[,4:ncol(df)], function(x) ifelse(as.numeric(x) > .8, paste0(x, "\\*"), x))
    
    df = dcast(setDT(df), timepoint ~ name, value.var = names(df)[grepl(target, names(df))], sep="_")

    if (target == "pow"){
        # Merge columns with same prefix (e.g., pow_int_V1_) as est (+1SE, -1SE)
        prefixes = c(unique(str_extract(names(df), "pow_int_V[0-9]+_")),
                    unique(str_extract(names(df), "pow_V[0-9]+_V[0-9]lag_"))
                    )
        prefixes = prefixes[!is.na(prefixes)]
    } else {
        prefixes = unique(str_extract(names(df), "PAP_[0-9].[0-9]*"))
        prefixes = prefixes[!is.na(prefixes)]
        prefixes = paste0(prefixes, "_")
    }


    for (prefix in prefixes) {
        df <- df %>%
            rowwise() %>%
            mutate(!!prefix := paste0(get(paste0(prefix, 'est')), "\n(", get(paste0(prefix, '-1SE')), ", ", get(paste0(prefix, '+1SE')), ")")) %>%
            ungroup()
    }
    df = df %>% select(-contains("est"), -contains("+1SE"), -contains("-1SE"))
    
    # Order based on timepoint
    # df$timepoint = as.numeric(df$timepoint)
    df <- df[order(df$timepoint),]

    # Pivot table
    if(pivot) df = df %>% gather(variable, value, -timepoint) %>% spread(timepoint, value)

    kbl(df, full_width = FALSE, escape = FALSE) %>%
        kable_classic() %>%
        row_spec(seq(1, nrow(df), 2), background = "lightgray")

}
```





## Tables {.tabset}


### Epskamp

```{r}
pow_table(df_res, "epskamp")
```

### bak2016_full

```{r}
pow_table_merge(df_res, "bak2016_full")
pow_table_merge(df_res, "bak2016_full", target="PAP", pivot=TRUE)
```

### bak2016_relapse

```{r}
pow_table_merge(df_res, "bak2016_relapse")
pow_table_merge(df_res, "bak2016_relapse", target="PAP", pivot=TRUE)
```

### bak2016_stable

```{r}
pow_table_merge(df_res, "bak2016_stable")
pow_table_merge(df_res, "bak2016_stable", target="PAP", pivot=TRUE)
```

### Illustration


```{r}
pow_table(df_res, "illustration")
```



# Power results

Display the lower timepoint value that has reached .8 over every model and parameter.
Note that:

- "500+": specify that power has not reached .8, even with Ttraining = 500.
- "-": specify that the power has not been computed for this parameter because it is not in the model.

```{r}
max_timepoint = max(df_res$timepoint)
df_res_pow = df_res %>%
    gather(par, pow, pow_int_V1:pow_V7_V7lag) %>%
    group_by(name, vars, par) %>%
    mutate(pow_reach = ifelse(pow >= .8 | timepoint == max_timepoint, 1, 0)) %>%
    filter(pow_reach==1) %>%
    slice(which.min(timepoint)) %>%
    mutate(T_pow = ifelse(is.na(pow), "-", ifelse(pow < .8, "500+",paste0(as.character(timepoint), " (", round(pow, 2), ")"))),
           par = str_remove(par, "pow_")) %>%
    ungroup() %>%
    dplyr::select(-c(vars,timepoint,sim_time, starts_with("PAP"), pow_reach, pow)) %>%
    spread(par, T_pow)

# df_res_pow %>% as.data.frame()

table_res_pow = kbl(df_res_pow) %>%
    kable_classic()

# Save kable
# save_kable(table_res_pow, "figures/outputs/table_res_pow.png")

table_res_pow
```




Plot the power curve for each model and parameters.

```{r, fig.height=20, fig.width=17}
p = df_res %>%
    gather(variable, power, starts_with("pow")) %>%
    mutate(variable = str_replace(variable, "pow_", "")) %>%
    ggplot(aes(y=power, x=variable, color=factor(timepoint), group=factor(timepoint))) +
        geom_line() +
        geom_point() +
        geom_hline(yintercept = .8) +
        facet_grid(name~.) +
        theme_bw() +
        theme(axis.text.x = element_text(angle = 90))

ggsave("figures/outputs/power_curve.png", plot=p)

p
```





# PAA results


The following table displays the SPAP score for each model and each R² targeted. 

```{r}
# Reshape dataframe to get a table
table_paa <- df_res %>%
    gather(paa, paa_score, starts_with("PAP")) %>%
    dplyr::select(c(dataset=name,variables=vars,timepoint,paa,paa_score)) %>%
    spread(timepoint, paa_score)

# Transform in kable and add a second header 
T_number <- ncol(table_paa) - 2
rows_grey <- c(outer(seq(1, nrow(table_paa), by = 6), 0:2, "+"))
table_paa <- kbl(table_paa) %>%
  kable_classic() %>%
  add_header_above(c(" " = 2, "T" = T_number)) %>%
  # Add row line every 3 rows
  row_spec(rows_grey, background = "lightgray")

# Save kable
# save_kable(table_paa, "figures/outputs/table_paa.png")

table_paa
```


The following plot displays the SPAP score for each model (colors) and each R² targeted (panels).

```{r}
breaks = unique(df_res$timepoint)

p = df_res %>%
    gather(paa, paa_score, starts_with("PAP")) %>%
    dplyr::select(c(name,vars,timepoint,paa,paa_score)) %>%
    ggplot(aes(y=paa_score, x= timepoint, color=name)) +
        geom_hline(yintercept = .8, color="red", alpha=.5) +
        geom_line() +
        geom_point() +
        scale_x_continuous(breaks = breaks) +
        scale_y_continuous(breaks = seq(0,1,.1)) +
        theme_bw() +
        facet_grid(paa~.)

ggsave("figures/outputs/paa_curve.png", plot=p)

p
```





